### 2021-07-19 doc/thesis/chapters/system-design-process.tex
validation / verification

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The SIMILAR Process}

@@

@@

In almost any kind of problem, there are multiple ways in order to archieve a successful solution.
However, some solutions may be preferred over others because of certain criteria that are evaluated.
Such criteria may be cost, risk, schedule or performance.
Based on the combined evaluation of these factors, a decision in favor of one selected alternative is made.\\

It is important to note that this step is a repeated step.
This is necessary, since there may only be a few known facts available at the initial intestigation.
Further design steps, such as a first estimation of the intended design implementation, simulation results, or a prototype can provide more data and facts.
These can be used to re-evaluate the alternatives and consequently optimize the design process.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Creation of a Problem Statement}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Concept Exploration}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The SIMILAR Process}
%TODO: maybe include additional facts from https://slideplayer.com/slide/14327503/

@@

Generally speaking, the problem statement serves the purpose to build a common understanding of the problem between a stakeholder and the developer.
In case there is a mismatch, an engineer may spend valuable time to develop a sophisticated solution to a problem that was not even a requirement.
Thus, any time spent to develop this feature is worthless, which highlights the importance of a correct problem statement.\\

@@

In almost any kind of problem, there are multiple ways in order to achieve a successful solution.
However, some solutions may be preferred over others because of certain criteria that are evaluated.
Such criteria may be cost, risk, schedule or performance.
Based on the combined evaluation of these factors, a decision in favor of one selected alternative is made.
This part of the process is also called concept exploration.\\

It is important to note that this step is a repeated, iterative step.
This is necessary, since there may only be a few known facts available at the initial intestigation.
Further design steps, such as a first estimation of the intended design implementation, simulation results, or a prototype can provide more data and facts.
These can be used to re-evaluate the alternatives and consequently optimize the design process.

@@

@@

The terms validation and verification are closely related, but have a different meaning in system design.

Validation fulfils the purpose to prove that the developed product does what it is intended to do.
It strives to build the \textit{right system}.
Verification on the other hand tries to build the \textit{system right}, by testing its properties against the previously determined specification and requirements.\\
